Adaptive group-regularized logistic elastic net regression

### 2019-03-22 docs/manuscript.Rnw

	For the regular elastic net, \texttt{gren}, \texttt{SGL}, \texttt{cMCP}, 
	and \texttt{gel}, we fix $\alpha \in \{0.05, 0.5, 0.95 \}$. In \texttt{gren}
	and the elastic net, $\alpha$ determines the proportion of $L_1$-norm penalty,
	such that the first setting closely resembles the ridge setting, 
	where $\alpha=0$, while the third setting is similar to the lasso with 
	$\alpha=1$. In \texttt{SGL}, \texttt{cMCP}, and \texttt{gel}, $\alpha$
	determines the ratio of group-level penalization ($\alpha=0$) to 
	feature level ($\alpha=1$) penalization. For the methods that do 
	automatic feature selection, we estimate models for a range of model sizes.

@@

>>>>

	For the regular elastic net, \texttt{gren}, \texttt{SGL}, \texttt{cMCP}, 
	and \texttt{gel}, we fix $\alpha \in \{0.05, 0.5, 0.95 \}$. In \texttt{gren}
	and the elastic net, $\alpha$ determines the proportion of $L_1$-norm penalty,
	such that the first setting closely resembles the ridge setting, 
	where $\alpha=0$, while the third setting is similar to the lasso with 
	$\alpha=1$. In \texttt{SGL}, \texttt{cMCP}, and \texttt{gel}, $\alpha$
	determines the ratio of group-level penalization ($\alpha=0$) to 
	feature level ($\alpha=1$) penalization. For the methods that do 
	automatic feature selection, we estimate models for a range of model sizes:
	$\hat{p} \in \{2, 4, 8, 16, 32, 64, 128, 256\}$.

@@

<<lines_simulations_res3_auc_briers, fig.cap="Estimated (a) AUC and (b) Brier skill score in simulation setting 3.", out.width="100%", fig.asp=1/2>>=
@

<<lines_simulations_res4_auc_briers, fig.cap="Estimated (a) AUC and (b) Brier skill score in simulation setting 4.", out.width="100%", fig.asp=1/2>>=
@

<<lines_simulations_res5_auc_briers, fig.cap="Estimated (a) AUC and (b) Brier skill score in simulation setting 5.", out.width="100%", fig.asp=1/2>>=
@
